Evolutionary stretegies

### 2015-12-02 evolutionaryComputation/notes4.tex
notes from fitfth lecture

>>>>

\section{Second practical}

MLS, ILS and GLS for graph Bipartioning.

the easiest thing to do is how long and see on waht
percentage they from the total??

Graph biportitioning, cut the graph into 2 groups
of 250

if the hamming distance is bigger than 2, just take
the complement of the 2?

\section{Knapsack}
Adaptive pursuit, pick one random with probability x, change
probability while running.

\section{Adaptive pursuit}
probability matching is used most often in literature, but its not
really that good.

Markov!

\subsection{Strategy}
the learning pase is a prarameter you have to play with.
